Parallel Adaptive Importance Sampling

### 2017-02-03 cover_letter.tex
cover letter edits

I am writing with regards to our previous submission to the SIAM/ASA Journal of Uncertainty Quantification, entitled ``Parallel Adaptive Importance Sampling''. Please forgive us for the length of this cover letter, but we felt strongly that we needed to address a few issues from our previous submission.

This manuscript had previously been submitted to the SIAM Journal for Scientific Computing, back in August 2015. We received 2 pretty positive reviews, although one review criticised our lack of a high dimensional example. The introduction at the time was possibly slightly misleading as application areas were mentioned (meteorology, oceanography, oil well diagnostic problems) where the unknowns in the inverse problem are high dimensional. We used these examples as these are the areas which are commonly used to motivate particle filters. Since our method uses a state-of-the-art resampler from a particle filter method, this felt like an appropriate setting for our method also. The particle filter methodology has a large literature, all of which uses these motivations, when in fact particle filters, like all importance sampling-based algorithms, suffer badly from the curse of dimensionality. 
%These papers often demonstrate their algorithm's efficacy by applying them to synthetic data sets arising from chaotic and low-dimensional dynamical systems, such as various iterations of the Lorenz equations. The criticisms that were levelled at our paper could just as well be applied to this entire thriving area of mathematical enquiry.

Unfortunately, one reviewer fixated on this, and as such we were asked not to resubmit unless we were able to demonstrate the performance of the algorithm in a very high dimensional setting, which of course is not feasible for this type of method. As such, we didn't feel that it would be worth our time in resubmitting to this particular journal.

As a result of this, we undertook a thorough rewrite of the paper, addressing as many of the other concerns of the referees as we could. We then considered which other journals would be a good fit for this work, and felt that SIAM UQ would be perfect. At this stage, we did make an error, in that when submitting, we failed to disclose the previous submission to SISC. In particular, we should have submitted a detailed description of the changes we had made to the manuscipt in response to the referee's comments. This is entirely our own error. However, SIAM's own policy dictates that any resubmissions to a different SIAM journal will be treated as a new submission. Unfortunately, our experience with this second submission has not reflected this.

>>>>

I am writing with regards to our previous submission to the SIAM/ASA Journal of Uncertainty Quantification, entitled ``Parallel Adaptive Importance Sampling''. Please forgive us for the length of this cover letter, but we felt that we needed to address a few issues from our previous submission.

This manuscript had previously been submitted to the SIAM Journal for Scientific Computing, back in August 2015. We received 2 pretty positive reviews, although one review criticised our lack of a high dimensional example. The introduction at the time was misleading as application areas were mentioned (meteorology, oceanography, oil well diagnostic problems) where the unknowns in the inverse problem are high dimensional. One reviewer focussed on this, and as such we were asked not to resubmit unless we were able to demonstrate the performance of the algorithm in a very high dimensional setting, which of course is not feasible for this type of method. As such, we didn't feel that it would be worth our time in resubmitting to this particular journal.

As a result of this, we undertook a thorough rewrite of the paper, addressing as many of the other concerns of the referees as we could, emphasising on low-dimensional but non-Gaussian distributions, one of which arises from inverse problems for biochemical networks. We then considered which other journals would be a good fit for this work, and felt that SIAM UQ would be perfect. The paper was substantially different, and as such we didn't view it as a simple resubmission to another journal. Our mistake was in not highlighting this in the coverletter to the submission to SIAM UQ.
